Meaningful data sharing

### 2020-08-25 new-paper.Rmd
remove . from title

---
title: Meaningful data sharing.
author: Nicholas J Tierney\* (1,2) & Karthik Ram\* (3)
output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
    includes:
      in_header: preamble.tex
bibliography: references.bib
header-includes: 
  - \setstretch{1.45}
  - \usepackage[utf8]{inputenc}
---

>>>>

---
title: Meaningful data sharing
author: Nicholas J Tierney\* (1,2) & Karthik Ram\* (3)
output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
    includes:
      in_header: preamble.tex
bibliography: references.bib
header-includes: 
  - \setstretch{1.45}
  - \usepackage[utf8]{inputenc}
---
